---
title: "Taxi Availability after New Year Countdown 2020"
output:
  rmarkdown::html_document:
    theme: yeti
date: "3 January 2020"
editor_options: 
  chunk_output_type: console
---

***

### Summary

- Data sourced from: datagovsgR, R package for accessing developer API tools
- Generally taxi availability increases throughout the day, with the lowest availability occuring at 0700
- Taxis tend to gather around the airport and town area

***

### 1. Set Up

```{r message = FALSE, warning = FALSE}
library(datagovsgR)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(ggmap)
library(gganimate)
```

```{r}
hours = c(0:23) %>% as.character() %>% str_pad(width = 2, pad = "0")
minutes = c(00,10,20,30,40,50) %>% as.character() %>% str_pad(width = 2, pad = "0")

output_df_all = data.frame()
```

* Allows for customisation of hours and minute intervals

<br>

### 2. Quering of data
  
```{r message = FALSE}
for (i in 1:length(hours)) {
  for (j in 1:length(minutes)) {
    
    input_date_time = paste("2020-01-01T", hours[i], ":", minutes[j], ":", "00", sep = "")
    output_df = taxi_availability(date_time = input_date_time) %>%
      mutate(date_time = paste("2020-01-01",hours[i], minutes[j], sep = ""))
    
    output_df_all = rbind(output_df_all, output_df)
  }
}

output_df_all$date_time = parse_date_time(output_df_all$date_time, orders = "Ymd HM")
```

* Quering API
* I chose to work in intervals of 10 minutes, on the first day of 2020

#### a. Graph of taxi availability over the 24 hour period

```{r}
avail_summary = output_df_all %>% 
  count(date_time)

ggplot(avail_summary, aes(y = n, x = date_time)) + 
  geom_point(col = "#26547c") +
  geom_line(col = "#26547c") + 
  labs(y = "Available Taxis", x = "Time") +
  theme_minimal()
```

* There appears to be a huge peak at midnight, and then a sharp drop over the next hour. This might be because of people heading home after the new year countdown.

* Generally, the taxi availability increases over the day, with the lowest around early morning and the rush hour, and the highest at midnight.

* The sharp drop in availability might be due to taxi bookings during the early morning rush hour.

#### b. Average availability by the hour

```{r}
avail_summary %>% 
  mutate(hour = hour(date_time)) %>%
  group_by(hour) %>%
  summarise(mean_n = mean(n)) %>%
  ggplot(aes(y = mean_n, x = hour)) + 
  geom_point(col = "#26547c") +
  geom_line(col = "#26547c") + 
  labs(y = "Available Taxis", x = "Time") +
  theme_minimal()
```

* Graphing by the hour shows a smoother graph, but we lose the peak at midnight noticed earlier. 

* General trend remains the same.

<br>

### 3. Taxi Locations

```{r message = FALSE}
register_google(key = Sys.getenv("GOOGLE_MAPS_API_KEY"))
sing <- get_map(location = "singapore",
                zoom = 11, 
                maptype = "terrain", 
                source = "google")
```

* To obtain the image of Singapore

```{r}
plot = ggmap(sing) + 
  geom_density_2d(aes(y = lat, x = long), data = output_df_all)
```

```{r eval = FALSE}
plot + 
  transition_time(date_time) + 
  labs(title = 'Date and Time: {frame_time}')
```

* Doesnt look very nice and looks very complicated
* Maybe it would be smoother if it was by the hour

```{r eval = FALSE}
output_df_all_hoursubset = output_df_all %>%
  filter(minute(date_time) == 0)

p = ggmap(sing) + 
  geom_density_2d(aes(y = lat, x = long), data = output_df_all_hoursubset) +
  labs(title = "{closest_state}") + 
  transition_states(date_time, transition_length = 0, state_length = 1)

g = output_df_all_hoursubset %>%
  count(date_time) %>%
  ggplot(aes(y = n, x = date_time)) + 
  geom_point() + 
  geom_line() +
  theme_minimal() +
  transition_reveal(date_time)

animate(p, fps = 25)
animate(g, fps = 25)
```

* To my understanding Rmarkdown knitting does not support these animations

***