---
title: "Taxi Availability after New Year Countdown 2020 Update"
output:
  rmarkdown::html_document:
    theme: yeti
date: "7 January 2020"
editor_options: 
  chunk_output_type: console
---

***

### Summary

- Data sourced from: datagovsgR, R package for accessing developer API tools
- Re-mapped taxi locations from a heat map, into a scale by locations

***

### 1. Set Up

```{r message = FALSE, warning = FALSE}
library(datagovsgR)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(ggmap)
library(gganimate)
library(sf)
library(tmap)
```

```{r eval = FALSE}
hours = c(0:23) %>% as.character() %>% str_pad(width = 2, pad = "0")
minutes = c(00,10,20,30,40,50) %>% as.character() %>% str_pad(width = 2, pad = "0")

output_df_all = data.frame()
```

* Same code as before

<br>

### 2. Quering of data
  
```{r message = FALSE, eval = FALSE}
for (i in 1:length(hours)) {
  for (j in 1:length(minutes)) {
    
    input_date_time = paste("2020-01-01T", hours[i], ":", minutes[j], ":", "00", sep = "")
    output_df = taxi_availability(date_time = input_date_time) %>%
      mutate(date_time = paste("2020-01-01",hours[i], minutes[j], sep = ""))
    
    output_df_all = rbind(output_df_all, output_df)
  }
}

output_df_all$date_time = parse_date_time(output_df_all$date_time, orders = "Ymd HM")
```

* Same code as before

<br>

#### a. Converting of objects into sf objects with the correct CRS

```{r eval = FALSE}
taxi_avail_sf = st_as_sf(output_df_all, 
                         coords = c("long", "lat"), 
                         crs = 4326)


sg = st_read(dsn = "shpfiles", 
             layer = "Planning_Area_Census2010", 
             stringsAsFactors=FALSE)
sg = st_transform(sg, crs = 4326)
sg = sg %>% 
  select(OBJECTID,
         AREA = PLN_AREA_N,
         REGION = REGION_N,
         X_ADDR,
         Y_ADDR,
         geometry)

```

* Importing the Singapore shape files, and converting the taxi locations into a `sf` object

#### b. Obtaining aggregates of the data

```{r eval = FALSE}
aggr_count = st_join(taxi_avail_sf, sg) %>% 
  count(date_time, AREA) %>% 
  as.data.frame(stringsAsFactors = FALSE) %>%
  select(date_time, AREA, n)

aggr_count = aggr_count %>% arrange(date_time)
```

* Using a spatial join to locate the towns in which each taxi was located in
* Using `count` then to find out the number of taxis for a given town and date time
* Sorted so that the loop in which the date time is used for plotting is in the correct order

<br>

#### c. Graphing the number of taxis for each given date time

```{r eval = FALSE}

for (i in 1:length(unique(aggr_count$date_time))) {
  
  input = aggr_count %>% filter(date_time == unique(aggr_count$date_time)[i])
  
  data = left_join(sg, input, by = "AREA")
  
  data$n[is.na(data$n)] = 0
  
  ggplot(data) + 
    geom_sf(aes(fill = n), show.legend = FALSE) + 
    scale_fill_viridis_c() +
    theme_void() + 
    labs(title = paste("Time: ", 
                       unique(aggr_count$date_time)[i] %>% 
                         hour() %>%
                         str_pad(width = 2, pad = "0"),
                       ":",
                       unique(aggr_count$date_time)[i] %>% 
                         minute() %>%
                         str_pad(width = 2, pad = "0"),
                       "\n",
                       "Number of Taxis: ",
                       sum(data$n),
                       sep = ""
                       ))
  
  ggsave(filename = paste("image", 
                          i %>% 
                            str_pad(width = 3, pad = "0"), 
                          ".png", 
                          sep = ""))
}
```

* Each of the 144 ggplots were saved as png images, padded so that they are in the correct order

<br>

```{r eval = FALSE}
file_names <- list.files(path = ".")

image_read(file_names) %>%
   image_animate(fps = 10)
```

* image_animate was used instead of using `ani_record()` as I could not make it work with the map files
* also `transition_time` does not appear to work with `geom_sf()`.

***








